---
title: "ProblemSet1"
author: "William Rebelsky"
date: "February 1, 2017"
output: html_document
---

```{r, message = FALSE}
library(rvest)
library(stringr)
```

#2Hours spent on coding, I have other classes

###Given a DOS-formatted text file (lines end with \r\n rather than just \n), convert it to a standard text file.
Assuming that I can get it into R, use str_replace_all
```{r}
file<-c("abc\r\ndef\r\ntexttestsarefun\r\n") 
str_replace_all(file, "\\r", "" )
```

####Given a standard text file, convert all uppercase letters to lowercase.
###Given a standard text file, remove all blank spaces at the end of lines.
Assuming that there is no other reason for there to be 3 spaces, and that these come before the \\n:
```{r}
file<-c("abc        \ndef      \ntext tests are fun.  Aren't They?       \n") 
str_replace_all(file, "\ \ \ (.+)\n","\n")
```

####Make a list of all misspelled words in a text file.

###Given a CSV file find the the five highest grades on homework 2.
Note that this is done through example due to time. (Figure out how to do something, then generalize)
```{r}
#Read the csv file
students<-read.csv("~/students.csv")
#Find the second homework
Homework2<-subset(students,students$Assignment==2)
#All we care about is the grades, so grab those
grades<-Homework2[,4]
#Sort the grades
sortedgrades<-sort(grades,decreasing = TRUE)
#Return the top 5
sortedgrades[1:5]
```

###Given an HTML file, find the URLs of all images.
Note that this is done through example due to time. (Figure out how to do something, then generalize)
```{r}
#Read the website
ImageParse <- read_html("https://en.wikipedia.org/wiki/Unix")
#create nodes for each image
ImageNodes <- html_nodes(ImageParse, "img")
#Get the important information without overwriting
ImageUrls1<-str_replace(ImageNodes, ".*src=\"(.+)\"","\\1")
ImageUrls2<-str_replace(ImageUrls1, "\ (.+)>","")
ImageUrls3<-str_replace(ImageUrls2, "\\\"","")
#Finish cleaning wikipedia's urls, if not wikipedia, may not need this
ImageUrls<-str_replace(ImageUrls3, "//","")
#Example
ImageUrls[1]
```

